Studying public transit API query logs\\ to get an indication of travel flows

### 2016-01-04 paper.tex

We researched these three initial questions on this dataset:
\begin{enumerate}
  \item How many queries were done monthly and how does this compare with the real number of passengers?
  \item How are the requests distributed within a day?
  \item Can we see deviations on an average request distribution on e.g., public holidays?
\end{enumerate}

@@

Next, we made a distribution of the requests done on each day of the week, which resulted in \cref{fig:average}.
In this chart we can spot, on Monday until Friday, the morning peak between 5 and 9 and the evening peak between 15 and 18.
We see a small dent during noon \todo{any explanation for this?}.
On Fridays we see that the morning peak is stronger than the morning peak, which can be explained by many students that go home to visit their parents for the weekend \todo{Can we give a link to more reading material about this behaviour? This might be weird for US people?}.
On Saturdays, we see almost do not see the peaks, which can be explained by people not going to work during weekends.
On Sundays, we see most requests happen in the evening, which can be explained by students going back to their student homes.

>>>>

We established three preliminary questions to  investigate the potential of this dataset:
\begin{enumerate}
  \item How many queries were done monthly and how does this compare with the real number of passengers?
  \item How are the requests distributed within a day?
  \item Can we see deviations on an average request distribution on e.g., public holidays?
\end{enumerate}

@@

Next, we made a distribution of the requests done on each day of the week, which resulted in \cref{fig:average}.
In this chart we can spot, on Monday until Friday, the morning peak between 5 and 9 and the evening peak between 15 and 18.
We see a small dent during noon \todo{any explanation for this?}.
On Fridays we see that the morning peak is stronger than the morning peak, which can be explained by many students that go home to visit their parents for the weekend \todo{Can we give a link to more reading material about this behaviour? This might be weird for US people?}.
On Saturdays, we almost do not see the peaks, which can be explained by people not going to work on weekends.
On Sundays, we see most requests happen in the evening, which can be explained by students returning to college accomodations.
